When the Pen Becomes a Sword: Retired US Military Officers and Op-Ed Use in Contemporary America

### 2020-07-14 code/Submissionv1.Rmd
commit

Finally, if one believes that today's polarization is different in degree and kind than previous eras of polarization, which has been argued in this paper, one must also recognize that the military will continue to face challenges as a result of political polarization. The events following the death of George Floyd certainly have revealed this.  
\singlespace
\pagebreak

>>>>

Finally, if one believes that today's polarized climate in America is different in degree and kind than previous eras of polarization, which has been a supporting claim of this paper, one must recognize that the military will face continued institutional challenges stemming from polarization's underlying causes. The most portending aspect regarding today's polarizing climate is that fundamental values are at stake, values that speak directly to the heritage of the United States as one nation under God and to the military as the nation's guarantor of rights and freedoms. As a non-partisan institution, the actions of the military will undoubtedly remain under scrutiny and close watch by the American public. No matter what it does, some will likely accuse the military of acting outside the bounds of the soldierly virtues of loyalty and duty. It is during these tough moments that moral courage will remain perhaps the chief attribute of military leaders, now and in the years to come. 
\singlespace
\pagebreak
